

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[hidelinks]{hyperref}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://gracethompson.ca/}{\Large Grace Thompson (RHCSA)}} & Email : \href{mailto:grace@gracethompson.ca}{grace@gracethompson.ca}\\
  \href{https://gracethompson.ca/}{https://www.gracethompson.ca} & Mobile : +1-(604)-999-2505 \\
\end{tabular*}




%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {SUSE}{North Vancouver, BC}
    {DevOps Engineer}{Sep. 2021 - Present}
    \resumeItemListStart
    \resumeItem{Observability}{Worked alongside other engineers and architects to improve observability and monitoring.}
    \resumeItem{Cloud}{Built out systems that automate infrastructure changes in a cloud environment.}
    \resumeItemListEnd
    \resumeSubheading
      {Global Relay}{Vancouver, BC}
      {Linux Systems Administrator}{Sep. 2020 - Aug. 2021}
      \resumeItemListStart
        \resumeItem{Ansible}
          {Developed and maintained Ansible code to automate routine tasks in a centralized fashion via an AWX instance running in a Docker container.}
        \resumeItem{Python}
          {Wrote Python scripts to parse through thousands of lines of data pulled from Red Hat Satellite and Red Hat IDM.}
        \resumeItem{Idempotency}
            {Replaced shell scripts with idempotent and easily manageable programs as member of Linux Automation Team.}
        \resumeItem{REST API}
        {Made a web interface with Django backend for the CEO to visualise the patching of servers in real time, with data pulled from the NetBox REST API.}

      \resumeItemListEnd

    \resumeSubheading
      {Insurance Corporation of British Columbia}{North Vancouver, BC}
      {Technical Support Specialist (Contract)}{May 2020 - Sep. 2020}
      \resumeItemListStart
        \resumeItem{Automation}
          {Created Python and PowerShell scripts to automate standard company processes, such as performing server health checks or pulling information from
vROps, ultimately resulting in a time savings of approximately one hour per morning.}



      \resumeItemListEnd

    \resumeSubheading
      {Orbis Investments}{Burnaby, BC}
      {Infrastructure Engineer}{Aug. 2019 - Mar. 2020}
      \resumeItemListStart
        \resumeItem{Troubleshooting}
          {Used PowerShell to provide assurance that a critical email had not been sent to the incorrect customer.}

      \resumeItemListEnd
\resumeSubheading
{British Columbia Institute of Technology}{Burnaby, BC}
{Junior Systems Analyst}{Jun. 2017 - Aug. 2019}
\resumeItemListStart
\resumeItem{Documentation}
{Co-ordinated the review of six hundred knowledge base articles, and worked with interns to update or re-write one hundred and sixty two of them.}
\resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Western Governors University}{Online}
      {Bachelor of Science in Computer Science}{Apr. 2021 -- Apr. 2025}
    \resumeSubheading
      {British Columbia Institute of Technology}{Burnaby, British Columbia}
      {Diploma in Computer Information Systems Administration }{Sep. 2016 -- Jun. 2018}
  \resumeSubHeadingListEnd
%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Name Generator}
      {Designed Go application to create fantasy names for writers and added Machine Learning with Python.}
    \resumeSubItem{Space Invaders}
      {Created Python version of the classic game Space Invaders.}
    \resumeSubItem{Youth Learn to Code}
      {Developed curricula and taught 3 separate classes to give young people in rural areas a chance to learn Python, Linux, and C\#.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Technical Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Operating Systems}{: RHEL | CentOS | SLES | Windows Server}
   }
   \item{
   \textbf{Software Development}{: Ansible | Puppet | Salt | Python | Go | Bash | PowerShell } 
   }
   \item{
   \textbf{Platforms}{: VMware vSphere | Docker | Kubernetes}
   }
   \item{
   \textbf{Networking}{: DNS | Routing | Switching | VLANs}
   }
   \item{
   \textbf{Cloud}{: AWS | Azure | GCP }
   }
 \resumeSubHeadingListEnd


%-------------------------------------------


\end{document}
